Topic modeling on EU and the USA research projects

### 2017-06-19 thesis_report/draft_thesis.tex
Update: Description of the computation of topic distribution over time

@@

!!!Write what you computed to get the results

@@

In figure X we plot the topic distribition over time. We can easily observe that
the topic 6, which refers to STEM education, is becoming a trend in the United
States over the years, while most of the other topics' evolution doesn't show up
such a high increace. Topics 5 and 8, which refer to Chemistry \& Materials
science and Molecular biology, respectively, show a small decreace over the
years.  +++

>>>>

In order to find the topic distribution over time, we need the topic
distribution of each project-document. As we mentioned before, LDA assumes that
each document exhibits multiple topics. After running the model to our dataset,
we get the document-topic distribution and we keep the topic with the highest
probability (the one that most likely belongs to this document). Then, we
calculate the proportion of each topic per FP, using the following equation:
\begin{equation}
topicProportion(k, fp) = \frac{\sum num of docs_{k,fp}}{\sum num of docs_{fp}} * 100
\end{equation}
where $k$ is the number of the topic id, $fp$ is the framework programme,
$fp \in [FP4, FP5, FP6, FP7, H2020]$. The topic proportion of each topic in 
the FP equals to the sum of the number of the documents assigned to this 
topic during the FP, nomralized by the number of the documents-projects 
occuring in this FP. In figure X we plot the results of the topic proportion 
over time.

@@

@@

Just like the computation in the EU dataset, we calculate the topic 
distribution over time for the USA dataset. We get the document-topic 
distribution, we keep the topic with the highest probability and finally 
we calculate the proportion of each topic per
year (instead of FP), using the following equation:

\begin{equation}
topicProportion(k, y) = \frac{\sum num of docs_{k,y}}{\sum num of docs_{y}} * 100
\end{equation}

where $k$ is the number of the topic id, $y$ is the year between 1994-2016. The
topic proportion of each topic per year equals to the sum of the number of the
documents assigned to this topic during the year, nomralized by the number of
the documents-projects  occuring in this year.

In figure X we plot the topic distribition over time. We can easily observe that
the topic 6, which refers to STEM education, is becoming a trend in the United
States over the years, while most of the other topics' evolution doesn't show up
such a high increace. Topics 5 and 8, which refer to Chemistry \& Materials
science and Molecular biology, respectively, show a small decreace over the
years. Topics 9 and 0 (Mechanical Engineering, Materiac Science and High energy
physics) show a small increase over the last 5 years. Mathematics' evolution
over time (Topic 1) looks stable on average and shows up as a popular subject
over the last 22 years, while Social Sciences and International Research (Topic
3 and 4) show a small decrease over the last 3 years.  Molecular biology and
Genetics (Topic 2) has an increasing polularity from 1994 to 2001 and later is
starting to stabilize. Climatology, Atmospheric and Ocean sciences look stable
the first years, while from 2006 up to date it is gradually becoming less
popular over the years.
